Fast sparse period estimation

### 2015-04-10 poster/ITR_Poster.tex
addition to icassp poster

@@

%%% title, author & contact %%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Noncoherent least squares estimators \\ of carrier phase and amplitude}
\author{Robby McKilliam, Andr\'{e} Pollok, Bill Cowley, \\ I. Vaughan L. Clarkson and Barry G. Quinn}
\newcommand{\email}{robby.mckilliam@unisa.edu.au}
\newcommand{\worksupportedby}{Supported under the Australian Government's Australian Space Research Program}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
	\centering
		\includegraphics[width=\linewidth]{../code/data/posterplot-2.mps}
		\caption{Phase mean square error for $4$-PSK (QPSK)}
		\label{fig:plotphaseM4}
\end{figure}

\vspace{0.79cm}
\begin{figure}
	\centering
		\includegraphics[width=\linewidth]{../code/data/posterplot-1.mps}
		\caption{Amplitude mean square error for $4$-PSK (QPSK)}
		\label{fig:plotampM4}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usetikzlibrary{pgfplots.groupplots}

@@

%%% title, author & contact %%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Fast sparse period estimation}
\author{Robby.~G.~McKilliam, I.~Vaughan.~L.~Clarkson and Barry.~G.~Quinn}
\newcommand{\email}{robby.mckilliam@unisa.edu.au}
\newcommand{\worksupportedby}{Supported under the Australian Government's Australian Space Research Program}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering 
  \begin{tikzpicture}
    \selectcolormodel{gray} 
    \begin{axis}[font=\footnotesize,xmode=log,ymode=log,height=15cm,width=25cm,xlabel={$N$},ylabel={time (ms)},ylabel style={at={(0.055,0.42)}},xlabel style={at={(0.5,0.1)}}, legend style={draw=none,fill=none,legend pos=north west,cells={anchor=west},font=\footnotesize}]
      \addplot[mark=o,mark options={scale=3}] table {../code/data/PeriodogramBenchmark};
      \addplot[mark=x,mark options={solid,fill=black,scale=3.6}] table {../code/data/LeastSquaresBenchmark};
      \addplot[mark=*,mark options={solid,fill=black,scale=1.5}] table {../code/data/QuantisedPeriodogramq4.0Benchmark};
      \addplot[mark=triangle,mark options={solid,fill=black,scale=2.7}] table {../code/data/QuantisedPeriodogramChirpZq4.0Benchmark};
      %\addplot[mark=square,color=black,mark options={solid,fill=black,scale=0.8}] table {code/data/SLS2novlpBenchmark};
      \addplot[mark=square,color=black,mark options={solid,fill=black,scale=2.4}] table {../code/data/SLS2newBenchmark};
      \legend{Periodogram, Least squares, Fast Fourier transform, Chirp z-transform, SLS-new}
   \end{axis}
  \end{tikzpicture}  
  \caption{Computation time in milliseconds versus $N$ for the periodogram, least squares, and quantized periodogram estimators computed using the chirp z-transform and a single fast Fourier transform.}\label{plot:benchmark}
\end{figure}

% \begin{figure}
% 	\centering
% 		\includegraphics[width=\linewidth]{../code/data/posterplot-2.mps}
% 		\caption{Phase mean square error for $4$-PSK (QPSK)}
% 		\label{fig:plotphaseM4}
% \end{figure}

% \vspace{0.79cm}
% \begin{figure}
% 	\centering
% 		\includegraphics[width=\linewidth]{../code/data/posterplot-1.mps}
% 		\caption{Amplitude mean square error for $4$-PSK (QPSK)}
% 		\label{fig:plotampM4}
% \end{figure}
